\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\setlength{\parindent}{0pt}

\begin{document}
\title{Progress Report 1}
\date{}
\maketitle
\section*{Project Title} 
Transmission Control System Design using CRIO Real Time Controller:
Data Gathering and Actuator Control
\section*{Team Members}
Group 35 \newline

\hangindent=17.62482pt
\hangafter=1
Shayan Ahmad \\
260350431 \\
shayan.ahmad@mail.mcgill.ca \newline

\hangindent=17.62482pt
\hangafter=1
Alejandro Carboni Jimenez \\
260523638 \\
alejandro.carbonijimenez@mail.mcgill.ca \newline

\hangindent=17.62482pt
\hangafter=1
Aditya Saha \\
260453165 \\
aditya.saha@mail.mcgill.ca

\section*{Supervisors}
\hangindent=17.62482pt
\hangafter=1
Yingxuan Duan PhD.\\ 
Research Associate\newline 

\hangindent=17.62482pt
\hangafter=1
Benoit Boulet PhD.\\
Associate Professor - Department of Electrical and Computer Engineering\\
Associate Chair - Operations

\newpage
\section*{Group Meetings with Advisor}
A preliminary group meeting was held on January 12th to establish the
strategy for this semester's work. \newline

A meeting was held with our immediate supervisor on January 13th. During the
meeting, short-term goals and the meeting schedule for the rest of the semester
was discussed. During the meeting, we also received feedback on our final 
deliveravbles from last semester. Following this meeting, follow-up meeting was
held to check our progress and verify the feasability of the new goals for 
this term.\newline

A last meeting was held with our supervisor on January 19th to demo the work
accomplished during the first work session. 

\section*{Project Readings}
There were no project readings identified since the previous report.

\section*{Recent Progress}
We continued our previous work on the CAN bus communication. An Arduino was set
up as a write node, and both an Arduino and a CAN handle connected to a laptop 
were set up as read nodes. Both two-node and 3 node systems were tested. 
Initial steps to read sensor data and transmit it over the CAN communication
channel were taken.\newline

We also added tools for collaborative report writing and source version control.
These tools will allow us to change the workflow to a more collaborative, 
end-goal based flow.

\section*{Future Plans}
For the following weeks, the plan is to further test configurations of the
communications links. This includes collision handling on a multiple write-node
network and priority message handling. Once the transmission of sensor data is
complete, the receiving Arduino node will have to respond by driving a circuit.
This circuit will be designed in conjunction with the supervisor. This response
will be used to close the feedback loop.

\section*{Group Work Report}
So far, the work has been adequately and fairly shared bewteen two team members,
Aditya and Alejandro. The third team member, Shayan Ahmad, has not been present
since the beginning of the term. We two are still awaiting an official notice
of his plans for the semester. The supervisor has been made aware of the
situation. At the moment of writing this report, he has not made any
contributions to the work.

\end{document}
