\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\setlength{\parindent}{0pt}

\begin{document}
\title{Progress Report 4}
\date{}
\maketitle
\section*{Project Title} 
Transmission Control System Design using CRIO Real Time Controller:
Data Gathering and Actuator Control
\section*{Team Members}
Group 35 \newline

\hangindent=17.62482pt
\hangafter=1
Shayan Ahmad \\
260350431 \\
shayan.ahmad@mail.mcgill.ca \newline

\hangindent=17.62482pt
\hangafter=1
Alejandro Carboni Jimenez \\
260523638 \\
alejandro.carbonijimenez@mail.mcgill.ca \newline

\hangindent=17.62482pt
\hangafter=1
Aditya Saha \\
260453165 \\
aditya.saha@mail.mcgill.ca

\section*{Supervisors}
\hangindent=17.62482pt
\hangafter=1
Yingxuan Duan PhD.\\ 
Research Associate\newline 

\hangindent=17.62482pt
\hangafter=1
Benoit Boulet PhD.\\
Associate Professor - Department of Electrical and Computer Engineering\\
Associate Chair - Operations

\newpage
\section*{Group Meetings with Advisor}
During this last period, there was one meeting held with our supervisor. This 
meeting was held to verify our progress, as well as to provide some basic 
information about the new force sensors we were provided. 

\section*{Project Readings}
The specifications of the force sensors were provided as readings for this 
period. 

\section*{Recent Progress}
During this period, the data logger module was revised and demonstrated to our
supervisor. The force sensor was studied and a framing circuit was designed. 

The compactRIO component was unavailable for integration this period. The
integration was pushed back until the next period. Work began on new content 
for the final report instead.

\section*{Future Plans}
During the next work period, the integration with the compactRIO will be 
attempted. The work on the GUI component will be continued. The force sensor 
circuit will be adequately tested and integrated with the Arduino. Work on 
the feedback loop of the overall system will begin this period.

\section*{Group Work Report}
So far, the Arduino tasks have been evenly split between two team members, 
Aditya and Alejandro. The third team member, Shayan, has been working remotely
on the GUI components of the project.

\end{document}
