\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\setlength{\parindent}{0pt}

\begin{document}
\title{Progress Report 1}
\date{}
\maketitle
\section*{Project Title} 
Transmission Control System Design using CRIO Real Time Controller:
Data Gathering and Actuator Control
\section*{Team Members}
Group 35 \newline

\hangindent=17.62482pt
\hangafter=1
Shayan Ahmad \\
260350431 \\
shayan.ahmad@mail.mcgill.ca \newline

\hangindent=17.62482pt
\hangafter=1
Alejandro Carboni Jimenez \\
260523638 \\
alejandro.carbonijimenez@mail.mcgill.ca \newline

\hangindent=17.62482pt
\hangafter=1
Aditya Saha \\
260453165 \\
aditya.saha@mail.mcgill.ca

\section*{Supervisors}
\hangindent=17.62482pt
\hangafter=1
Yingxuan Duan PhD.\\ 
Research Associate\newline 

\hangindent=17.62482pt
\hangafter=1
Benoit Boulet PhD.\\
Associate Professor - Department of Electrical and Computer Engineering\\
Associate Chair - Operations

\newpage
\section*{Group Meetings with Advisor}
There were no direct meetings held with our supervisor during this period. 
However, email correspondence was used to track progress and determine the
next step of our work.

\section*{Project Readings}
There were no readings identified this week.

\section*{Recent Progress}
Since the previous progress report, a data-logging module was implemented
using one of the available Arduinos. The data-logging module was connected to
the same CAN bus as the other modules, and their interoperability was verified.

As the force sensor was not yet available to us, a simple template of the data
gathering module associated to it was created. The appropriate handling of
data format was foreseen.

\section*{Future Plans}
During this next period, we plan on receiving a force sensor and integrating
its analog data into the digital communication network. We also plan to begin
working on establishing the connection between the Arduino-based nodes and 
the CompactRIO based module, depending on its availability.

\section*{Group Work Report}
So far, the Arduino tasks have been evenly split between two team members, 
Aditya and Alejandro. Since the previous progress report, the third team member,
Shayan, contacted the supervisor and has been assigned tasks he can complete 
remotely, while working on the same overall project. These tasks are related
to the Graphical User Interface (GUI) that will display desired system
state parameters. 

\end{document}
